---
title: "p8105_hw1_bg2604"
author: "Boya Guo"
date: "09/21/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


```{r Question_1.1}
set.seed(123)
q1_df = tibble(
  x = runif(10, min = 0, max = 5),
  vec_logical = x > 2,
  vec_char = c("Q", "W", "E", "R","T","Y","U","I","O","P"),
  vec_factor = factor(c("girl", "boy", "girl", "boy","girl", "boy", "girl", "boy","girl", "boy"))
)
q1_df

mean(q1_df$x)
mean(q1_df$vec_logical)
mean (q1_df$vec_char)
mean(q1_df$vec_factor)
```

The mean of numeric and logical variables could be run, but not characer or factor variables. 

```{r Question_1.2}
as.numeric(q1_df$vec_logical)
as.numeric(q1_df$vec_factor)
as.numeric(q1_df$vec_char)
```

Logical and factor variables could be converted, but not character variables.

```{r Question_1.3}
as.numeric(as.factor(q1_df$vec_char))
as.numeric(as.character(q1_df$vec_factor))
```
After converting character variable from character to factor to numeric, it was converted successfully. However, I could not convert my factor variable from factor to character to numeric (NA shown up).





